ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-01-12 paper.tex
more additions about features and dataset comparisons

\title{ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images}
\author{Alexander Groleau\inst{1,2} \and
  Kok Wei Chee\inst{1} \and
  Jonathan Boarman\inst{1} \and
  Samay Maini\inst{1}}

@@

\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
  \and
  Left Associates LLC (\email{research@left.associates})}

@@

\section{Introduction}
Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, ree of noise or other degradations. ShabbyPages is a large dataset composed of 6153 clean/noisy pairs of images taken from 600 digital documents. Information about the set's contents and its relation to other datasets are explored in the next section. The noisy images were created from their clean origins by the application of a pipeline developed with the Augraphy library; the production of ShabbyPages is detailed in the third section, with all source code and input materials made openly available. The final dataset is used to train several denoising models which are compared directly and whose prediction results are compared together in the final section.

@@

\begin{figure}
\includegraphics[width=\textwidth]{Article_Hero_Picture_Shadow.png}
\caption{Example ShabbyPages image, with the groundtruth partially augmented on the right.} \label{fig1}
\end{figure}

\subsection{Features}
Modern artificial neural networks produce a latent representation of their training data, a space from which outputs are sampled. In deep networks, these representations live within multiple layers, each of which corresponds to a feature of the input data. Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents.\\

Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.

\begin{table}
\centering
\caption{Document Image Dataset Feature Comparison}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Feature & ShabbyPages & NoisyOffice & RVL-CDIP & Tobacco800 \\
\hline
Images & 6153 & 72 & 400000 & 1290\\
Document-specific & Yes & Yes & Yes & Yes\\
Synthetic & Yes & Yes & No & No\\
Groundtruthed? & Yes & Yes & No & No\\
Font size & Multiple & 16pt & Multiple & Multiple\\
Paper styles & Multiple & 1 & Multiple & Multiple\\
Multilingual & Yes & No & No & No\\
Documents contain images? & Yes & No & Yes & Yes\\
Pre-categorized & No & No & Yes & Yes\\
\hline
\end{tabular}
\end{table}

@@

\subsection{Tobacco800}
Tobacco800, like RVL-CDIP, is a subset of the Complex Document Image Processing collection, containing images of documents originally internal to tobacco companies, and released under the Tobacco Master Settlement Agreement. The corpus is composed of 1290 images, gathered and scanned at different times and by different devices. Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}. Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.

\subsection{Statistics}
ShabbyPages contains documents from multiple classes, which contain many types of information.

@@

\begin{table}
\centering
\caption{ShabbyPages Statistics}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Statistic & Value \\
\hline
Images & 6153 \\
DPI & 150 \\
Max image size & \_ \\
\hline
\end{tabular}
\end{table}

\subsection{Limitations}
The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.

First, we arbitrarily selected 600 as the number of source documents. The number of final images of pages depends on this, and so is similarly arbitrary.

@@

\section{Motivation for Denoising}
TODO

@@

\subsection{Data Gathering}
A team of workers searched the public internet for PDFs of many different kinds. 600 unique documents were retrieved, totaling 6153 pages. A similar process was completed to collect paper textures on which to "print" the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses. Care was taken to retrieve freely-available and attributable documents; a CSV file containing document and paper texture links (as of time of download), with their sources, is available and distributed with the dataset. We also manually reviewed the gathered documents to verify that no personal identity information was present within the corpus.

@@

Processing all 6153 images took TODO:TIME on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.

@@

\

@@

\bibitem{ref_DocCreator}
  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
\bibitem{ref_fastai}
\end{thebibliography}
\end{document}

>>>>

\title{ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images}
\author{Alexander Groleau\inst{1,2} \and
  Kok Wei Chee\inst{1} \and
  Stefan Larson\inst{3} \and
  Jonathan Boarman\inst{1} \and
  Samay Maini\inst{1}}

@@

\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
  \and
  Left Associates LLC (\email{research@left.associates})
  \and
  Vanderbilt University}

@@

\section{Introduction}
Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations. ShabbyPages is a large dataset composed of 6202 clean/noisy pairs of images taken from 600 digital documents. Information about the set's contents and its relation to other datasets are explored in the next section. The noisy images were created from their clean origins by the application of a pipeline developed with the Augraphy library; the production of ShabbyPages is detailed in the third section, with all source code and input materials made openly available. The final dataset is used to train several denoising models which are compared directly and whose prediction results are compared together in the final section.

@@

\begin{figure}
\includegraphics[width=\textwidth]{Article_Hero_Picture_Shadow.png}
\caption{Example ShabbyPages image, before and after augmentation.} \label{fig1}
\end{figure}

\subsection{Features}
Modern artificial neural networks produce a latent representation of their training data, a space from which outputs are sampled. In deep networks, these representations live within multiple layers, each of which corresponds to a feature of the input data. Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents, making their internal representations by neural networks often quite complicated.\\

Networks with a wider variety of latent representations frequently perform better when generalizing their learned functions to other tasks. Procuring a large-enough volume of robust-enough training data is paramount. Several sets of such images exist, many intended for processing by deep neural nets; Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.\\

\begin{table}
\centering
\caption{Document Image Dataset Feature Comparison}\label{tab1}
\begin{tabular}{|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|}
\hline
Feature & ShabbyPages & NoisyOffice & RVL-CDIP & Tobacco800 \\
\hline
Images & 6202 & 72 & 400000 & 1290\\
Document-specific & Yes & Yes & Yes & Yes\\
Synthetic & Yes & Yes & No & No\\
Groundtruthed? & Yes & Yes & No & No\\
Font size & Multiple & 16pt & Multiple & Multiple\\
Paper styles & Multiple & 1 & Multiple & Multiple\\
Multilingual & Yes & No & No & No\\
Documents contain images? & Yes & No & Yes & Yes\\
Pre-categorized & No & No & Yes & Yes\\
\hline
\end{tabular}
\end{table}

@@

\subsection{Tobacco800}
Tobacco800, like RVL-CDIP, is a subset of the Complex Document Image Processing collection, containing images of documents originally internal to tobacco companies, and released under the Tobacco Master Settlement Agreement. The corpus is composed of 1290 images, gathered and scanned at different times and by different devices. Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}. Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.\\

Every document in the ShabbyPages groundtruth set is a multi-page document. The released set was exported at 150 DPI, but the original documents are also distributed, so re-exporting at a higher resolution is trivial. The smallest image is 532 by 532, with the largest 3336 wide by 12157 tall. 6202 images are present in ShabbyPages, but this number could easily be increased by simply running another Augraphy pipeline to generate more.

\subsection{ShabbyPages Compared}
Supervised learning tasks require labeled training data, called the ground truth. Much of the world's data does not come with labels, which instead must be created by humans in some fashion. In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined. This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_goldmann}, \cite{ref_zenodo} and Tobacco800 \cite{ref_tobacco800gt1}, \cite{ref_tobacco800gt2}, but the images in these sets were produced by real scans, without an accompanying original digital document. Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.\\

ShabbyPages includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully reproducing the ShabbyPages set, allowing anyone to quickly produce a new set in the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand. The 6202 images in the ShabbyPages release set are really just the first sample from the space of these documents; we encourage building your own. NoisyOffice is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the NoisyOffice training data. Augraphy's PaperFactory augmentation is such a tool. The other sets are not even theoretically extensible in this way.

\subsection{Statistics}
ShabbyPages contains documents from multiple classes, which contain many types of information.\\

@@

\begin{table}
\centering
\caption{ShabbyPages Statistics}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Statistic & Value \\
\hline
Images & 6202 \\
DPI & 150 \\
Max image size & \_ \\
\hline
\end{tabular}
\end{table}

\subsection{Limitations}
The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.\\

First, we arbitrarily selected 600 as the number of source documents. The number of final images of pages depends on this, and so is similarly arbitrary.\\

@@

@@

\subsection{Data Gathering}
A team of workers searched the public internet for PDFs of many different kinds. 600 unique documents were retrieved, totaling 6202 pages. A similar process was completed to collect paper textures on which to "print" the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses. Care was taken to retrieve freely-available and attributable documents; a CSV file containing document and paper texture links (as of time of download), with their sources, is available and distributed with the dataset. We also manually reviewed the gathered documents to verify that no personal identity information was present within the corpus.

@@

Processing all 6202 images took TODO:TIME on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.

@@

\section{Motivation for Denoising}
Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it. Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, or when our aesthetic sensibilities aren't injured.\\

@@

\bibitem{ref_DocCreator}
  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
\bibitem{ref_goldmann}
  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
\bibitem{ref_zenodo}
  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
\bibitem{ref_tobacco800gt1}
  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger. Multi-scale Structural Saliency for Signature Detection. In Proc. IEEE Conf. Computer Vision and Pattern Recognition (CVPR 2007), pp. 1‐8, 2007.}
\bibitem{ref_tobacco800gt2}
  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}

\end{thebibliography}
\end{document}
